Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 Experiments.tex
New figures and new data -- experiments

Experiments consist in running AthenaMP instances by using NGE pilots where each AthenaMP simulates a pre-determined number of events taken from ATLAS workload.	
We present four groups of experiments in which we test the NGE for weak scalability, weak scalability with resubmission, strong scalability and heterogeous workloads.

@@

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakStart1.pdf}
    \caption{Average time to start running AthenaMP for pilot sizes: 250, 500, 1000 and 2000.}
\label{fig:weakScal1b}
\end{figure}

\subsubsection{Weak scalability with resubmission }
This experiment is similar to the one presented above but in this case we want to test also the impact of submitting new AthenaMP instances in place of those that end. The reason behind this experiment is to stress pilot's components by pushing new tasks while others are ending their execution.

@@

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakET2.pdf}
    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:weakScal2a}
\end{figure}
\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakStart2.pdf}
    \caption{Average time to start running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:weakScal2b}
\end{figure}
\subsubsection{Strong scalability}
This experiments aim to test strong scalability. Therefore, we run the same amount of tasks for different pilot sizes. 
We used a number of AthenaMP instances equal to 2048 and tested pilots with 256, 512, 1024 and 2048 nodes. 
Each AthenaMP instance simulates sixteen events as the previous experiment.

@@

%\begin{figure}[!htb]
%        \includegraphics[width=0.5\textwidth]{./figures/NGE/strongET.pdf}
%    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
%\label{fig:strongScala}
%\end{figure}
%\begin{figure}[!htb]
%        \includegraphics[width=0.5\textwidth]{./figures/NGE/strongStart.pdf}
%    \caption{Average time to start running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
%\label{fig:strongScalb}
%\end{figure}

@@

The last experiment provides a proof of concept about the ability of the NGE to execute heterogeneous workload.
In particular, we coupled the execution of AthenaMP with the execution of Gromacs to simulate molecular dynamics. 
We performed the experiment by executing at first one AthenaMP per node and then, submitting a Gromacs simulation per core. Each Gromacs simulation requires ~20 minutes.
We tested the following pilot sizes : 8, 32, 64.

>>>>

Experiments consist in running AthenaMP instances by using NGE pilots where each AthenaMP simulates a pre-determined number of events taken from ATLAS workload.	
We present four groups of experiments in which we test the NGE for weak scalability, weak scalability with multiple generation, strong scalability and heterogeous workloads.

@@

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakOver1.pdf}
    \caption{Average overhead running AthenaMP for pilot sizes: 250, 500, 1000 and 2000.}
\label{fig:weakScal1b}
\end{figure}

\subsubsection{Weak scalability with multiple generation }
This experiment is similar to the one presented above but in this case we want to test also the impact of submitting new AthenaMP instances in place of those that end. The reason behind this experiment is to stress pilot's components by pushing new tasks while others are ending their execution.

@@

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakET2.pdf}
    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:weakScal2a}
\end{figure}
\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/weakOver2.pdf}
    \caption{Average overhead running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:weakScal2b}
\end{figure}
\subsubsection{Strong scalability}
This experiments aim to test strong scalability. Therefore, we run the same amount of tasks for different pilot sizes. 
We used a number of AthenaMP instances equal to 2048 and tested pilots with 256, 512, 1024 and 2048 nodes. 
Each AthenaMP instance simulates sixteen events as the previous experiment.

@@

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/strongET.pdf}
    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:strongScala}
\end{figure}
\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/strongOver.pdf}
    \caption{Average overhead running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:strongScalb}
\end{figure}

@@

The last experiment provides a proof of concept about the ability of the NGE to execute heterogeneous workload.
In particular, we coupled the execution of AthenaMP with the execution of Gromacs to simulate molecular dynamics. 
We performed the experiment by executing at first one AthenaMP per node and then, submitting a Gromacs simulation per core. Each Gromacs simulation requires ~20 minutes.
We tested the following pilot sizes : 8, 16, 32, 64.

\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/MDET.pdf}
    \caption{Average pilot execution time against average AthenaMP execution times  for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:strongScala}
\end{figure}
\begin{figure}[!htb]
        \includegraphics[width=0.5\textwidth]{./figures/NGE/MDOver.pdf}
    \caption{Average overhead running AthenaMP for pilot sizes: 256, 512, 1024 and 2048.}
\label{fig:MDScal}
\end{figure}
